\clearpage
\begin{landscape}

\fontsize{10}{12}\selectfont

\begin{xltabular}{\linewidth}{| p{1.8cm} | X | X | X | X | X |}
\hline
\multicolumn{1}{|c}{\multirow{2}{*}{\textbf{Criteria}}} &
  \multicolumn{5}{c|}{\textbf{Standard}} \\ \cline{2-6} 
\multicolumn{1}{|c}{} &
  \multicolumn{1}{c|}{\textbf{Advanced (35)}} &
  \multicolumn{1}{c|}{\textbf{Proficient (28)}} &
  \multicolumn{1}{c|}{\textbf{Developing (23)}} &
  \multicolumn{1}{c|}{\textbf{Emerging (16)}} &
  \multicolumn{1}{c|}{\textbf{No Evidence (0)}} \\ \hline
\endhead
%
\textbf{System\newline Scope\newline 20\%} &
MVP's originally proposed functional \& non-functional requirements, or those agreed and documented early in the project, are fully delivered. &
MVP's originally proposed functional \& non-functional requirements, or those agreed and documented early in the project, are delivered with small variances. &
MVP's functional \& non-functional requirements were revised and documented later in the project, and are mostly delivered. &
MVP's functional \& non-functional requirements underwent significant revision late in the project, and are mostly delivered. Or, little revision was done, but some significant requirements are delivered. &
MVP's functional \& non-functional requirements underwent significant revision late in the project, and are partially delivered. Or, little revision was done, and significant requirements are not delivered. \\
\hline
\textbf{Architecture\newline Suitability\newline 20\%} &
Delivered architecture, supplemented by the design reflection, is very well suited to delivering all key functional \& non-functional requirements. &
Delivered architecture, supplemented by the design reflection, is mostly suited to delivering all key functional \& non-functional requirements. &
Delivered architecture, supplemented by the design reflection, is fairly well suited to delivering most key functional \& non-functional requirements. &
Delivered architecture, supplemented by the design reflection, should deliver some key functional \& non-functional requirements. &
Delivered architecture, supplemented by the design reflection, may deliver one or two key functional \& non-functional requirements. \\
\hline
\textbf{Testing\newline Quality\newline 20\%} &
All key functional \& non-functional requirements, \& key architectural components are well tested (or are described adequately in a test plan) and, where feasible, are mostly automated. &
Most key functional \& non-functional requirements, \& key architectural components are well tested (or are described adequately in a test plan) and, where feasible, are mostly automated. &
Most key functional \& non-functional requirements, \& key architectural components are fairly well tested (or are described fairly adequately in a test plan) and, where feasible, many are automated. &
Main test cases for a few key functional \& non-functional requirements, \& key architectural components are fairly well tested (or have some meaningful description in a test plan) and, where feasible, some are automated. &
Testing is poor, superficial or extremely limited. There are very few, if any, automated tests. \\
\hline
\textbf{Architecture\newline Description\newline 20\%} &
Accurate, clear and complete description of all aspects of the architecture. Narrative text and diagrams complement each other. Views support describing all aspects of the architecture. Decisions about trade-offs are well described within the context of the design discussion. &
Accurate, clear and mostly complete description of the architecture. Narrative text and diagrams complement each other. Views support description of the architecture. Decisions about important trade-offs are well described within the context of the design discussion. &
Mostly accurate and fairly complete description of the architecture. Narrative text and diagrams support each other. Decisions about some important trade-offs are adequately described within the context of the design discussion. &
Some parts of the description are inaccurate or incomplete. Most diagrams are relevant to the narrative text or a necessary diagram is missing. Few trade-offs are adequately described within the context of the design discussion. &
Many parts of the description are inaccurate or incomplete. Few diagrams are relevant to the narrative text or many necessary diagrams are missing. Trade-offs are poorly described. \\
\hline
\textbf{Architecture\newline Evaluation\newline 20\%} &
Critique \& evaluation clearly demonstrate that the delivered architecture, varied a little by the reflection comments, can deliver all functional \& non-functional requirements of the full system. &
Critique \& evaluation fairly clearly demonstrate that the delivered architecture, varied by the reflection comments, can deliver all functional \& non-functional requirements of the full system. &
Critique \& evaluation imply fairly well that the delivered architecture, varied by the reflection comments, might deliver most functional \& non-functional requirements of the full system. &
Critique \& evaluation demonstrate that the delivered architecture, varied by the reflection comments, is unlikely to deliver some key functional or non-functional requirements of the full system. &
Critique \& evaluation demonstrate that the delivered architecture, varied by the reflection comments, is unlikely to deliver most functional or non-functional requirements of the full system. Or, they are too unclear to determine. \\
\hline
\end{xltabular}

\clearpage
\end{landscape}