\clearpage
\begin{landscape}

\section*{Cloud-Infrastructure Assignment Criteria}

\fontsize{9}{11}\selectfont

\begin{xltabular}{\linewidth}{| P{1.5cm} | X | X | X | X | X | X | X |}
\hline
\multicolumn{1}{|c}{\multirow{2}{*}{\textbf{Criteria}}} &
  \multicolumn{7}{c|}{\textbf{Standard}} \\ \cline{2-8} 
\multicolumn{1}{|c}{} &
  \multicolumn{1}{c|}{\textbf{Exceptional ~ (7)}} &
  \multicolumn{1}{c|}{\textbf{Advanced ~ (6)}} &
  \multicolumn{1}{c|}{\textbf{Proficient ~ (5)}} &
  \multicolumn{1}{c|}{\textbf{Functional ~ (4)}} &
  \multicolumn{1}{c|}{\textbf{Developing ~ (3)}} &
  \multicolumn{1}{c|}{\textbf{Little Evidence ~ (2)}} &
  \multicolumn{1}{c|}{\textbf{No Evidence ~ (1)}} \\ \hline
\endhead
%
\textbf{API Functionality\newline 10\%} &
API passes at least \textcolor{red}{85\%} of the full test suite, including all valid GET, POST~\&~PUT requests, \& persistence. &
API passes at least \textcolor{red}{75\%} of the full test suite, including most valid GET requests with complex queries, all valid POST \& PUT requests, \& persistence. &
API passes at least \textcolor{red}{65\%} of the full test suite, including some valid GET requests with complex queries, at least valid POST requests, \& persistence. &
API passes at least \textcolor{red}{50\%} of the full test suite. &
API passes at least \textcolor{red}{40\%} of the full test suite. &
API passes at least \textcolor{red}{20\%} of the full test suite. &
API passes less than \textcolor{red}{20\%} of the full test suite. \\
% 2023 Criteria for 2 and 1.
%API responds to the healthcheck or \textcolor{red}{10\%} of the test suite. &
%API is unable to be built or does not respond to requests. \\
\hline

\textbf{Deployed to Cloud\newline 10\%} &
Deployed API passes at least \textcolor{red}{85\%} of the full test suite, including  all valid GET, POST \& PUT requests, \& persistence. &
Deployed API passes at least \textcolor{red}{75\%} of the full test suite, including most valid GET requests with complex queries, all valid POST \& PUT requests, \& persistence. &
Deployed API passes at least \textcolor{red}{65\%} of the full test suite, including some valid GET requests with complex queries, at least valid POST requests, \& persistence. &
Deployed API passes at least \textcolor{red}{50\%} of the full test suite. &
Deployed API passes at least \textcolor{red}{40\%} of the full test suite. &
Deployed API passes at least \textcolor{red}{20\%} of the full test suite. &
Deployed API passes less than \textcolor{red}{20\%} of the full test suite. \\
% 2023 Criteria for 3, 2 and 1.
%Deployment creates individual resources which are able to serve an HTTP endpoint. 
%Deployment creates individual resources which are unable to serve an HTTP endpoint. 
%API cannot be deployed. \\
\hline

\textbf{Scalable Application\newline15\%} &
Nearly all complex scenarios are handled well.
Resources have been used efficiently (scale up \& down). &
Most complex scenarios are handled well.
Resources have been used efficiently (scale up \& down). &
A few complex scenarios are handled,
or resource usage is not efficient (scale down is implemented poorly). &
Simple scenarios are handled well.
or resource usage is not efficient (scale down is not implemented). &
Some simple scenarios have been handled well. &
Minimal simple scenarios are handled. &
No scenarios are handled. \\
\hline
\end{xltabular}

\end{landscape}
