\documentclass{slide}

\title{Software Architecture}
\subtitle{CSSE6400}
\author{Richard Thomas}
\date{The Future}

\begin{document}

\maketitle

\question{What is \highlight{Software Architecture}?}

\point{\highlight{Software Architecture} is hard to define.}

\point[Let's hear from an expert]{\centering \youtubevideo{images/making-architecture-matter-thumb}{https://www.youtube.com/watch?v=DngAZyWMGR0}}

\definition[Okay so...]{Software Architecture}{The important stuff; whatever that is.}

\question{What do \highlight{you} want from this course?}

\definition[Maybe...]{Software Architecture: The Course}%
{The set of tools, processes, and design patterns which enable quality attributes to be met in software.}

\question{What are \highlight{Quality Attributes}?\extra{Hint: CSSE3002 / CSSE3012}}

\begin{frame}{Quality Attributes}

Non-functional requirements for the success of software.

\end{frame}

\begin{frame}{Quality Attributes: Examples}

\begin{description}[<+->]
    \item[Modularity] Components of the software are separated into \highlight{discrete modules}.
    \item[Availability] The software is \highlight{available to access} by end users, either at any time or on any platform, or both.
    \item[Scalability] The software is \highlight{simultaneously usable} by a large amount of end users.
    \item[Extensibility] Features or extensions can be \highlight{easily added} to the base software.
    \item[Testibility] The software is designed so that \highlight{automated tests} can be easily deployed.
\end{description}

\end{frame}

\point[Problem]{Software cannot meet all quality attributes.}

\point[``Solution'']{Software architects prioritize the important attributes.\extra{on a software-by-software basis}}

\definition{The First Law of Software Architecture \cite{richards2020fundamentals}}{Everything in software architecture is a trade-off.}

\definition{Wicked Architecture \cite{wicked-architecture}}%
{There are often \highlight{no clear problem descriptions}, \highlight{no clear solutions},
good or bad solutions, \highlight{no clear rules} when to ``stop'' architecting
and mostly team rather than individual work.}

\point[Why now?]{Architecture is more important today thanks to \highlight{expectations} and \highlight{infrastructure}.}

\todo{End it gracefully}

\references{articles,books}

\end{document}