\documentclass{csse4400}

\title{Security Principles}
\author{Brae Webb}

\date{{\color{red} The Future}}

\begin{document}

\makecover

\maketitle

\section{Introduction}

One quality attributes which developers often overlook is security.
Security can be the cause of a great deal of frustration for developers;
there are no comfortable architectures, nor command-line tools to magically make an application secure.
As the world depends on technology more than ever while, at the same time the impacts of cyber attacks become more devastating,
it has become crystal clear that security is everyones responsibility.
As users of technology, as developers, and as architects, we all need to ensure we take security seriously.

Learning, and for that matter, teaching, how to make software secure is no easy task.
Every application has different flaws and risks, every attack vector and exploit is unique; managing to keep up with it all is daunting.
None of us will ever be able to build a completely secured system but that is no reason to stop trying.
As developers and architects, security should be an on-going process in the back of your minds.
A nagging voice which constantly asks `what if?'.

We introduce security first to set the example.
As we go through this course, the principle of security will recur again and again.
With each architecture introduced, we will stop and ask ourselves `what if?'.
In your future careers, you should endeavour to carry this same practice.
Each feature, pipeline, access control change, or code review, ask yourself, `what are the security implications?'.

With that said, there are some useful principles, and a handful of best practices which we will explore.
But again, even if you follow these practices and embody the principles,
you will still be hopeless insecure, unless,
you are constantly reflect on the security implications of your each and every decision.

\section{The Self}
Before we even fantasize about keeping our applications secure, let's review if you're secure right now.
As developers we often have heightened privileges and access, at times above that of even the CEOs.
If you aren't secure, then nor is anything you work on.
Let's review some of the basics.

\textbf{Keep your software up to date.}
Are you running the latest version of your operating system?
The latest chrome, or firefox, or god-forbid, internet explorer?
If not then there is a good chance you are currently at risk.
Software updates, while annoying, provide vital patches to discovered exploits.
You must to keep your software up to date.

\textbf{Use multi-factor authentication.}
This should be hard to explain to a grandmother but this should be obvious to software developers.
One million passwords are stolen every week \cite{password-security}.
If you don't have some sort of multi-factor authentication enabled, hackers can access your account immediantly after stealing your password.

\textbf{Use a password manager.}
Following from the startling statistic of a million stolen passwords, we must seriously consider how we use passwords.
Our practices should be guided by the fact that at least one service we use likely stores our password insecurely.
We should assume that our password will be compromised.
What can we do about this?
The first thing is to avoid password reuse, one password per service.
Of course, humans have very limited memory for remembering good passwords.
So go through and update your passwords with randomly generated secure passwords and then, store them in a password manager.


\section{Principles of Securing Software}
Okay, now that we're not a security risk ourselves, we can start considering securing the software we develop.
Before looking at pragmatic practices, we'll develop a set of guiding principles.
These principles are far from comprehensive but they provide a useful foundation to enable discussion of our security practices.

\subsection{Principle of Least Privilege}
\subsection{Principle of Separation of Duties}
\subsection{Principle of Defense in Depth}
\subsection{Principle of Failing Securely}
\subsection{Principle of Open Design}
\subsection{Principle of Avoiding Security by Obscurity}
\subsection{Principle of Minimizing Attack Surface Area}


\section{Practices of Secure Software}





\begin{drafting}
\begin{itemize}
    \item introduce security
    \item security is an on-going process
    \item best kept in the back of your head
    \item you will never be completely secure, but that shouldn't stop you trying
    \item couple of useful principles
    \begin{itemize}
        \item principle of least privilege
        \item principle of separation of duties
        \item principle of defense in depth
        \item principle of failing securely (facebook example)
        \item principle of open design (2310)
        \item principle of avoiding security by obscurity
        \item principle of minimizing attack surface area
    \end{itemize}
    \item couple of best practices
    \begin{itemize}
        \item sanitizing inputs
        \item use encryption where reasonable
        \item keep software up to date
        \item use MFA
        \item use firewalls
        \item track your systems
        \item use a password manager
        \item be smart, trust but verify
    \end{itemize}
    \item when in doubt, hire an expert
\end{itemize}
\end{drafting}


\bibliographystyle{plain}
\bibliography{articles}


\end{document}